Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2020-08-08 ms/sections/results.tex
new figure on why did archipelago wide machines detect anything

The small archipelago-wide effect of habitat-type was detected for PC1, PC2 and PC3 (mixed-effect ANOVA with island as a random effect, Table \ref{suptab:anova-pooled}), but this effect was too small for \textit{post hoc} tests to find which habitats differed. Archipelago-wide differences in dewlap coloration between habitats were also detected by SVMs trained on pooled data regardless of island identity, both for PCA data and reflectance scores (Fig. \ref{supfig:classif-svm-pca-pooled}, \ref{supfig:classif-svm-refl-pooled}). This pattern seemed to be driven by mangrove lizards being correctly reassigned more often than predicted by chance. Sensitivity analyses on these machines suggest a relatively small role of long wavelengths (red reflectance) in driving this pattern (Fig. \ref{supfig:importance-svm-refl-pooled}) -- \textbf{be more explicit about how the colors vary among habitats} --, but did not reveal strong differences between the PCs in relative importance (Fig. \ref{supfig:importance-svm-pca-pooled}).  Archipelago-wide differences were not detected by LDA classifiers at all (Fig. \ref{supfig:classif-lda-pca-pooled}, \ref{supfig:classif-lda-refl-pooled}).\\ %So, the differences could be in something other than means.\\

>>>>

The small archipelago-wide effect of habitat-type was detected for PC1, PC2 and PC3 (mixed-effect ANOVA with island as a random effect, Table \ref{suptab:anova-pooled}), but this effect was too small for \textit{post hoc} tests to find which habitats differed. Archipelago-wide differences in dewlap coloration between habitats were also detected by SVMs trained on pooled data regardless of island identity, both for PCA data and reflectance scores (Fig. \ref{supfig:classif-svm-pca-pooled}, \ref{supfig:classif-svm-refl-pooled}). This seemed to be driven primarily by mangrove lizards being correctly reassigned more often than predicted by chance. Sensitivity analyses on these machines suggest that wavelengths from a large range, between 300 and 600nm, overall played a more important role in successful identification than wavelengths above 600nm (Fig. \ref{supfig:importance-svm-refl-pooled}), and that PC3 and PC4 were more important than PC2 (Fig. \ref{supfig:importance-svm-pca-pooled}). This suggests that archipelago-wide differences may involve fine deviations from the main axes of variation (such as PC2) in multiple wavelengths, and possibly nonlinear combinations of wavelengths, that only the SVMs, not the LDAs, could pick up (Fig. \ref{supfig:classif-lda-pca-pooled}, \ref{supfig:classif-lda-refl-pooled}). This pattern was weak, with machine accuracy scores narrowly distributed around about $50\%$, which is suggestive of only small deviations and a large degree of overlap in color space (Fig. \ref{supfig:pooled} and \ref{supfig:reflectance-pooled}).\\
